Title

### 2013-01-31 inc/magnetic_lenses/maglens.tex
continuing to move \section directives into subimported files
added magnetic lens picture

@@

>>>>

\section{Magnetic Lenses} \label{sec:mag_lens}

@@

A picture of this system is shown in \ref{fig:maglens-pic}.
In that picture the two lenses are shown, however a placeholder is inserted between them rather than the RF cavity.

\begin{figure}
  \centering
  \includegraphics{maglens.jpg}
  \caption{
    Side view of the two custom large-bore magnetic lenses designed and built at UIC, seen installed in the prototype UEM.
    The coils are visible as is high permeability shielding used for the pole-piece.
    The outer (larger) plates and struts are for structural integrity only.
  }
  \label{fig:maglens-pic}
\end{figure}
